---
title: "Introduction to sc19097"
author: "Shen maoquan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to sc19097}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__sc19097__ is a simple package including two R functions and one C function. The first function(pe1.R) is to use  Parseval theorem Leibniz formula to calculate the order value of pi. The second is to use Leibniz formula(pe2.R) to calculate the order value of pi.In addition, the generating program of Gibbs(gibbsC.cpp) is written in C + +.And put the assignment of this semester in Vignette.


## pe1  Parseval theorem

The source R code for _pe1_ is as follows:
```{r,eval=FALSE}
pe1<-function(n){
  z<-numeric(n)
for(i in 1:n){
  z[i]<-8*(1/(2*i-1)^2)
}
y<-sqrt(sum(z))
y

}
```

## pe2  Leibniz formula

```{r,eval=FALSE}
pe2<-function(n){z<-numeric(n)
for(i in 1:n){
  z[i]<-4*(-1)^(i+1)/(2*i-1)
}
x<-sum(z)
x
}
```
pe1 and pe2 functions can be used to compare the convergence of the two methods for calculating the pi.
## gibbsC.cpp  for Exercise9.4


```{r,eval=FALSE}
NumericMatrix gibbsC(int N, int thin) {
  NumericMatrix mat(N, 2);
  double x = 0, y = 0;
  for(int i = 0; i < N; i++) {
    for(int j = 0; j < thin; j++) {
      x = rgamma(1, 3, 1 / (y * y + 4))[0];
      y = rnorm(1, 1 / (x + 1), 1 / sqrt(2 * (x + 1)))[0];
    }
    mat(i, 0) = x;
    mat(i, 1) = y;
  }
  return(mat);
}
}
```


